---
title: 'Appendix 4: Mixed-effect models of match advantages'
#tags: `PSA002`
output: html_document
#header-includes:
#  - \usepackage{caption}
#  - \usepackage{float}
#  - \captionsetup[table]{name=Table S,labelsep = period}
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lme4)
library(lmerTest)
library(ggplot2)
library(sjPlot)

# Import multiple-bytes string in English system
Sys.setlocale("LC_ALL","English") 
```




```{r load_info, message=FALSE, warning=FALSE, include=FALSE}
# Load lab information
lab_info <- ##dirname(getwd()) %>%
  dir(path = "..",full.names = TRUE, recursive = TRUE, include.dirs = TRUE, pattern = "Lab_info.csv")  %>%
  read_csv()

lab_fin <- ##dirname(getwd()) %>%
  dir(path = "..",full.names = TRUE, recursive = TRUE, include.dirs = TRUE, pattern = "lab_fin.csv")  %>%
  read_csv()

# Load meta data of in site data: age, female numbers

insite_meta <- dir(path = "..",full.names = TRUE, recursive = TRUE, include.dirs = TRUE, pattern = "insite_meta.csv") %>%
  read_csv() 

# Load and summary meta data of online data: age, female numbers, language proficiency
osweb_meta <- dir(path = "..",full.names = TRUE, recursive = TRUE, include.dirs = TRUE, pattern = "jatos_meta.csv") %>%
  read_csv() %>%
  mutate(gender = ifelse(gender==1,"FEMALE",ifelse(gender==2,"MALE","OTHER"))) %>%
  mutate(birth_year = as.numeric(birth_year)) %>%
  mutate(year = ifelse(birth_year > 21 & !is.na(birth_year), 1900 + birth_year, 2000 + birth_year)) %>%
  mutate(age = ifelse(!is.na(year),2021-year,NA)) %>%
  group_by(Batch) %>%
  summarise(N = n(), Female_N = sum(gender=="FEMALE",na.rm = TRUE), Age = round(mean(age, na.rm=TRUE),0), Proficiency = round(mean(lang_prof),0) )

SP_V <-  dir(path = "..",
      pattern = "all_rawdata_SP_V",   ## include in-site and internet data
      recursive = TRUE, full.names = TRUE) %>% 
      read_csv() %>%
      subset(correct == 1 & Match != "F") %>%  ## Exclude the incorrect responses and filler trials
      inner_join(select(lab_info, PSA_ID, Language), by = "PSA_ID") %>%
    distinct() %>% ## Merge the language aspects
    mutate(Language = ifelse(Language == "Magyar", "Hungarian", Language)) %>%  ## Switch "Magyar" to "Hungrian"
    mutate(Language = ifelse(Language == "Simple Chinese", "Simplified Chinese", Language)) %>%  ## Switch "Simple Chinese" to "Simplified Chinese"
    mutate(Source = if_else(opensesame_codename == "osweb","osweb","site"), 
           Subject = paste0(Source,"_",PSA_ID,"_",subject_nr)) ## Compose the unique participant id

```



```{r outlier-check, message=FALSE, warning=FALSE, include=FALSE, paged.print=TRUE}
get_intercept <- function(set) {
  #Subject = as.factor(subset(SP_V_tidy,PSA_ID == LAB_ID)$Subject) %>% levels() %>% as.numeric()
  
# Source = as.factor(subset(SP_V_tidy,PSA_ID == LAB_ID)$Source) %>% levels() %>% as.numeric()

 #Subject = paste(Source,"_",subject_nr)
 
  t <- cbind(#Source,
             #subject_nr,
             Subject = levels(as.factor(set$Subject)),
             (lmer(response_time ~ Match + (1|Subject), data = set) %>%
  coef())$Subject %>%
      as.tibble()%>%
  mutate(Outlier = `(Intercept)` > quantile(`(Intercept)`,probs=.75))
    )
  
  return(t)
}

LABS <- unique(SP_V$PSA_ID)

outliers_table <- NULL
for(lab_id in LABS){
  outliers_table<- get_intercept( subset(SP_V,PSA_ID == lab_id)) %>%
    mutate(LAB = lab_id) %>%
    rbind(outliers_table)
}
```

```{r SP-lme-data, message=FALSE, warning=FALSE, include=FALSE}
# export data file for the making of appendix
SP_V_lme_data <- dir(path = "..",
      pattern = "SP_V_lme_data.csv",   ## include in-site and internet data
      recursive = TRUE, full.names = TRUE) %>% 
      read_csv() %>%
  inner_join(subset(outliers_table, Outlier == FALSE),by = c("Subject","PSA_ID" = "LAB"))

SP_V_lme_data$Language <- ifelse(SP_V_lme_data$Language == "Magyar","Hungarian",SP_V_lme_data$Language) 
SP_V_lme_data$Language <- ifelse(SP_V_lme_data$Language ==  "Simple Chinese", "Simplified Chinese", SP_V_lme_data$Language)

SP_V_lme_data <- mutate(SP_V_lme_data,
                        Match = factor(Match,
                          levels = c("Y","N"),
                          labels = c("MATCHING","MISMATCHING")),
                        Source = factor(Source, 
                       levels = c("site","osweb"),
                       labels = c("Site","Internet") ))
```

### Planned analysis: Matching was the only one independent variable

1. The model with four random effects: participants, targets, laboratories, and languages.


```{r SP_effect01_lme, message=FALSE, warning=FALSE, results='asis'}
SP_all_random.lmer = lmer(response_time ~ Match + (1|Subject) + (1|Target) + (1|PSA_ID) + (1|Language), data = SP_V_lme_data) ## build mixed-effects regression

tab_model(SP_all_random.lmer, title = "Coefficients")
```

2. The model excluded the targets and languages from the random effect structure. The final report decided `SP_reduced_random.lmer` the best fitted model.

```{r SP_effect02_lme, message=FALSE, warning=FALSE}
SP_reduced_random.lmer = lmerTest::lmer(response_time ~ Match + (1|Subject) + (1|PSA_ID), data = SP_V_lme_data)
SP_slope_nocor_reduced_random.lmer = lmer(response_time ~ Match + (1|Subject) + (Match||PSA_ID), data = SP_V_lme_data)
SP_slope_cor_reduced_random.lmer = lmer(response_time ~ Match + (1|Subject) + (Match|PSA_ID), data = SP_V_lme_data)

tab_model(SP_reduced_random.lmer)
tab_model(SP_slope_nocor_reduced_random.lmer)
tab_model(SP_slope_cor_reduced_random.lmer)
```


### Models included data source

We evaluated the interaction of match advantage and data collection sources in three models. Based on the recommended practices(Barr et al., 2013; Brauer & Curtin, 2018), the models used the optimizer `bobyqa`. The final report decided `source_cor.lmer` the best fitted model.

```{r SP_source_lme, message=FALSE, warning=FALSE, cache=TRUE}
## standardized
SP_V_lme_data$r_Source = if_else(SP_V_lme_data$Source == "Site",1,0)

source_zero_slope_nocor.lmer =lmer(response_time ~ Match*r_Source + (1|Subject) + (1|PSA_ID) + (1|Language), 
  control = lmerControl(optimizer = "bobyqa",
                        optCtrl = list(maxfun = 1e6)), data = SP_V_lme_data)


source_nocor.lmer =lmer(response_time ~ Match*r_Source + (1|Subject) + (r_Source||PSA_ID) + (r_Source||Language), 
  control = lmerControl(optimizer = "bobyqa",
                        optCtrl = list(maxfun = 1e6)), 
   data = SP_V_lme_data)

source_cor.lmer =lmer(response_time ~ Match*r_Source + (1|Subject) + (r_Source|PSA_ID) + (r_Source|Language), 
  control = lmerControl(optimizer = "bobyqa",
                        optCtrl = list(maxfun = 1e6)), 
                        data = SP_V_lme_data)

tab_model(source_zero_slope_nocor.lmer)

tab_model(source_nocor.lmer)

tab_model(source_cor.lmer)

```


### Models included languages 


We analyzed the interactions by the data sources separately.

#### on site data


We evaluated the interaction of match advantage and languagess in three models. Based on the recommended practices(Barr et al., 2013; Brauer & Curtin, 2018), the models used the optimizer `bobyqa`. The final report decided `lang_cor.lmer` the best fitted model.

```{r SP_lang_site_lme, message=FALSE, warning=FALSE}
## Check sample size of a language by site data
site_excluded_lang <- subset(SP_V_lme_data, Source=="Site") %>%
  group_by(Language, Subject) %>%
  summarise(N_trials = n()) %>%
  group_by(Language) %>%
  summarise(N = n()) %>%
  filter(N < 25) %>%
  pull(Language)

## Allocate the site data
SP_V_lang_lme_data = subset(SP_V_lme_data, Source=="Site" & !(Language %in% site_excluded_lang))

## Run the mixed effect model by site data
lang_cor.lmer =lmer(response_time ~ Language*Match + (1|Subject), 
  control = lmerControl(optimizer = "bobyqa",
                        optCtrl = list(maxfun = 1e6)), 
  data = SP_V_lang_lme_data)

lang_slope_nocor.lmer =lmer(response_time ~ Language*Match + (Match||Subject), 
  control = lmerControl(optimizer = "bobyqa",
                        optCtrl = list(maxfun = 1e6)), data = SP_V_lang_lme_data)

lang_slope_cor.lmer =lmer(response_time ~ Language*Match + (Match|Subject), 
  control = lmerControl(optimizer = "bobyqa",
                        optCtrl = list(maxfun = 1e6)), data = SP_V_lang_lme_data)


tab_model(lang_cor.lmer)  
tab_model(lang_slope_nocor.lmer)
tab_model(lang_slope_cor.lmer)
```


#### web-based data


We evaluated the interaction of match advantage and languagess in three models. Based on the recommended practices(Barr et al., 2013; Brauer & Curtin, 2018), the models used the optimizer `bobyqa`. The final report decided `osweb_cor.lmer` the best fitted model.


```{r SP_lang_osweb_lme, message=FALSE, warning=FALSE, cache=TRUE}
## Check sample size of a language by osweb data
osweb_excluded_lang <- subset(SP_V_lme_data, Source=="Internet") %>%
  group_by(Language, Subject) %>%
  summarise(N_trials = n()) %>%
  group_by(Language) %>%
  summarise(N = n()) %>%
  filter(N < 25) %>%
  pull(Language)  ## Exclude the languages less than 25 participants

## Allocate the osweb data
SP_V_osweb_lme_data = subset(SP_V_lme_data, Source=="Internet" & !(Language %in% osweb_excluded_lang))


## Run the mixed effect model by site data
osweb_cor.lmer = lmerTest::lmer(response_time ~ Language*Match + (1|Subject), 
  control = lmerControl(optimizer = "bobyqa",
                        optCtrl = list(maxfun = 1e6)), # Increase maximum number of iterations to facilitate model convergence , 
        data = SP_V_osweb_lme_data)

osweb_slope_nocor.lmer =lmer(response_time ~ Language*Match + (Match||Subject), 
  control = lmerControl(optimizer = "bobyqa",
        optCtrl = list(maxfun = 1e6)), data = SP_V_osweb_lme_data)

osweb_slope_cor.lmer =lmer(response_time ~ Language*Match + (Match|Subject), 
  control = lmerControl(optimizer = "bobyqa",
        optCtrl = list(maxfun = 1e6)), data = SP_V_osweb_lme_data)


tab_model(osweb_cor.lmer)
tab_model(osweb_slope_nocor.lmer)
tab_model(osweb_slope_cor.lmer)
```